\textbf{ A purely kinematic distance to the Galactic Center }

### 2018-07-28 paper/gc.tex
sag -> sgr
no hyphen
note to self

% jargon macros
\newcommand{\sagastar}{Sag\,A$^{\ast}$}

@@

\begin{abstract}\noindent
% Context
The distance from the Sun to the Galactic Center is a critical parameter
that sets the length scale for many Galactic measurements and phenomena.
Radio observations have delivered an extremely precise proper motion
of the Center (or really \sagastar),
but not a distance with comparable precision.
Meanwhile, the \gaia\ Mission is delivering distances and proper motions for
billions of stars, some of which extend to $>10$~kpc.
% Aims
Here we produce a purely kinematic measurement of the position of the
Galactic Center.
% Methods
We use the \gaia\ data to calibrate accurate but simple data-driven
spectrophotometric distance estimates to luminous red-giant stars.
We compare the mean proper motions of these stars as a function of distance
and azimuth in the Milky-Way disk to the azimuth and proper motion of
\sagastar.
% Results
We find a kinematic distance to the Galactic Center of $XXX\pm YYY$~kpc.
This distance measurement is purely kinematic and geometric;
it involves no physical or dynamical model of either stars or the Milky Way.
\end{abstract}

@@

>>>>

% jargon macros
\newcommand{\sagastar}{Sgr\,A$^{\ast}$}

@@

\begin{abstract}\noindent
% Context
The distance from the Sun to the Galactic Center is a critical parameter
that sets the length scale for many Galactic measurements and phenomena.
Radio observations have delivered an extremely precise proper motion
of the Center (or really \sagastar),
but not a distance with comparable precision.
Meanwhile, the \gaia\ Mission is delivering distances and proper motions for
billions of stars, some of which extend to $>10$~kpc.
% Aims
Here we produce a purely kinematic measurement of the position of the
Galactic Center.
% Methods
We use the \gaia\ data to calibrate accurate but simple data-driven
spectrophotometric distance estimates to luminous red-giant stars.
We compare the mean proper motions of these stars as a function of distance
and azimuth in the Milky Way disk to the azimuth and proper motion of
\sagastar.
% Results
We find a kinematic distance to the Galactic Center of $XXX\pm YYY$~kpc.
This distance measurement is purely kinematic and geometric;
it involves no physical or dynamical model of either stars or the Milky Way.
\end{abstract}

@@

What do we know about the Galactic Center distance? And cite the GRAVITY result.
